Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-07-05 pkg/disttree/inst/draft/draft.Rnw
corrections of the notation in the appendix based on reviews
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2207 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: c611cfca307dec01674a360cb58c46458a3f21f2

>>>>

The breakpoint that leads to the highest discrepancy between score functions 
in the two resulting subgroups is selected as split point. 
This is measured by the linear statistic
$$
T_{l^{\ast}}^r = \min_{s=1,2}\sum_{i \in \mathcal{B}_{sr}} s(\bm{\hat{\theta}}, Y_i)
$$
where $\mathcal{B}_{1r}$ and $\mathcal{B}_{2r}$ are the two new subgroups, without 
any particular ordering, that 
are defined by splitting in split point $r$ of variable $Z_{l^{\ast}}$. 
The split point is then chosen as follows:
$$
r^{\ast} = \argmin_{r} c(t_{l^{\ast}}^r,\mu_{j^{\ast}}^r,\Sigma_{l^{\ast}}^r).
$$
One repeats the testing and splitting procedure in each of the resulting 
subgroups until some stopping criterion is reached. This criterion 
can for example be a minimal number of observations in a node or a 
minimal $p$-value for the statistical tests. In that way pre-pruning
is applied in order to find right-sized trees and hence 
avoid overfitting.
